Presentation Title

### 2017-07-13 thesis/chapters/ch1-intro.tex
Finish some TODOs
Thanks Quinten

We live in a world where technologies have become vital for our welfare and success.
The internet, for instance, gave us the ability of efficiently exchange information on a global scale.
However, in contrast to its original design, the internet and in particular the world wide web is becoming increasingly centralised.
The domain name system, certificate authorities, to name a few, carry enormous responsibilities and are a central point of failure.
The  same can be said for many other services such are online marketplaces,
cloud services, hospitality services and even our banking system.
The 2008 financial crisis is an example of the banking system making poor choices which result in a
decline in consumer wealth in the order of trillions~\cite{financialcrisis} and led to the European debt crisis.

Ironically, also in 2008, Satoshi Nakamoto published the Bitcoin whitepaper~\cite{bitcoin}.
Which, for the first time, gave us a simple banking system in the form of a distributed ledger.
It needs no central control but still incorruptable even if there are malicious parties that aim to undermine the system.
We call such a ledger a blockchain.

The primary innovations are (1) its consensus model which prevents double spending,
and (2) its incentive mechanism that encourages anyone (with adaquate hardware) to participate in the network and keep it running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
At some instant in time, $A$ sees that $C$ transferred 5 units to $A$ and $B$ sees that $C$ transferred 5 units to $B$.
Hence the transaction is inconsistent with respect to the observer.
Bitcoin and many other blockchain systems solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is reach agreement on a set of valid values, e.g. transactions. 
This effectively eliminates inconsistencies.
In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work}.
Where miners (parties that runs the Bitcoin network) collect transactions and compete in solving (using brute force) a difficult puzzle.
The first miner to solve it generates a block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block, that is the solution of the puzzle,
depends on the previous block.
Hence the name blockchain.
Further, honest miners always work on the largest chain.
Due to the difficulty of the puzzle,
it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market cap, at the time of writing, is over 40 billion USD~\cite{bitcoinmarketcap}.
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{todo}, heath care~\cite{todo}, logistics~\cite{todo}, energy~\cite{todo} and so on.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to hit the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network.
It also requires a hard fork (not backward compatible), which risks consensus failure and devaluation.
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size may help.
But given the bandwidth and latency constraints,
it not possible to have more than 758 transactions per second.
Even worse, it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa~\cite{visa},
which is in the order of tens of thousands transactions per second.

@@

% However, not everyone is convinced on the practicality of blockchain systems.
% Bram Cohen, the inventor of BitTorrent said
% ``It's getting a lot more media attention than the actual impact it's having so far.''~\cite{cohen}
% Forbes listed a few reasons on why we should be skeptical about blockchains~\cite{forbes},
% some of them include its accessibility for the layperson and its scalability issues.

>>>>

We live in a world where technologies have become vital for our welfare and success.
The internet, for instance, gave us the ability of efficiently exchange information on a global scale.
However, in contrast to its original design, the internet and in particular the world wide web is becoming increasingly centralised.
The domain name system (root name server), certificate authorities (root CA), to name a few, carry enormous responsibilities and are a central point of failure.
The  same can be said for many other services such are online marketplaces,
cloud services, hospitality services and even our banking system.
The 2008 financial crisis is an example of the banking system making poor choices which result in a
decline in consumer wealth in the order of trillions~\cite{financialcrisis} and led to the European debt crisis.

Ironically, also in 2008, Satoshi Nakamoto published the Bitcoin whitepaper~\cite{bitcoin}.
Which, for the first time, gave us a simple banking system in the form of a distributed ledger.
It needs no central control but still incorruptable with high probability even if there are malicious parties that aim to undermine the system.
We call such a ledger a blockchain.

The primary innovations are (1) its consensus model which prevents double spending,
and (2) its incentive mechanism that encourages anyone (with adaquate hardware) to participate in the network and keep it running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
At some instant in time, $A$ sees that $C$ transferred 5 units to $A$ and $B$ sees that $C$ transferred 5 units to $B$.
Hence the transaction is inconsistent with respect to the observer.
Bitcoin and many of its derivatives (e.g. Litecoin\footnote{\url{litecoin.org}} and Dogecoin\footnote{\url{dogecoin.org}}) solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is reach agreement on a set of valid values, e.g. transactions. 
This effectively eliminates inconsistencies.
In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work}.
Where miners (parties that runs the Bitcoin network) collect transactions and compete in solving (using brute force) a difficult puzzle.
The first miner to solve it generates a block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block, that is the solution of the puzzle,
depends on the previous block.
Hence the name blockchain.
Further, due to the difficulty of the puzzle and that the majority of the parties are honest,
it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market cap, at the time of writing, is over 40 billion USD~\cite{bitcoinmarketcap}.
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{finance}, heathcare~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to hit the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network.
It also requires a hard fork (not backward compatible), which risks consensus failure and devaluation.
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size may help.
But given the bandwidth and latency constraints,
it not possible to have more than 758 transactions per second.
Even worse, it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa~\cite{visa},
which is in the order of tens of thousands transactions per second.

@@

### 2017-07-13 thesis/chapters/ch2-problem.tex
Thanks Quinten

Blockchain technology has many advantages over centralised systems.
Its decentralised and democratic nature removes central point of control or failure.
However, as we described in the Introduction, it faces a genuine scalability problem.
In particular, proof-of-work based systems are unlikely to reach the transaction rate of Visa even with parameter tuning.
What we wish to see is horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
Hence, the research question we answer in this  work is the following.
\begin{displayquote}
\emph{Is it possible to design a blockchain fabric that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}

In order to make sense of our research question, we must first define \emph{blockchain fabric}.
Typical blockchain systems are application specific.
For example, the application in Bitcoin (any many others) is digital cash, the application in Namecoin is domain name registration~\cite{namecoin} and the application in Siacoin is cloud storage~\cite{siacoin}.
Underneath these applications lies the blockchain fabric, which we call the consensus protocol, and it is abstract over the application.
In the case of Bitcoin it is proof-of-work (PoW) because PoW is not concerned with the structure of the transactions,
it works by simply treating transactions as a blob of data and hashes them with the previous block.
Hence, we wish to design an application neutral system.
It should act as a backbone that provides the building blocks of any blockchain based applications.
Also, it should be possible to build any kind of application on top our system.
We do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

In the remainder of this chapter we expand on our research question and visit each of our requirement in detail and discuss our approach.

@@

The first objective is to reach consensus on a global \emph{state}.
We emphasise the word state because in contrary to traditional blockchains,
it does not neccessarily mean the set of all transactions that has ever happened.
The state can be a verifiable representation of all the transactions.
As an extreme example, a single digest of the complete history can represent the state.
It is even verifiable as long as there are nodes that stores the history.

Traditional blockchain systems use PoW as the consensus algorithm,
but consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
consensus algorithms have existece since the 80s~\cite{pease1980reaching, lamport1982byzantine}.
The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
The authors show that running PBFT in Network File System (NFS) was only 3\% slower than the standard unreplicated NFS.
Since then, research in this area picked up pace and many more algorithms are introduced~\cite{abd2005fault, kotla2007zyzzyva}.
With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

Our approach is to combine the vast literature in Byzantine fault tolerance research with blockchain technology,
and introduce a new consensus model to record the global state.

@@

There is another aspect of fault tolerance that is transaction verifiability.
Recall that it is not neccessary to reach consensus on all the transactions in order to record the state.
But when using some digest (or a set of digets) to represent the state, it is also important for the transactions to be verifiable.
Otherwise adversaries could simply store invalid transactions in the state and they would never be detected.

@@

The last but not least, the final objective is horizontal scalability.
We wish to see the performance (global transaction rate) increase as more nodes join the network.
BitTorrent~\cite{cohen2003incentives} is an example of such a system,
where peers interact with eachother to exchange files without any global bottleneck.

@@

\section{Limitations}
Our work removes the transaction bound from the blockchain.
However, the price to pay is that the Sybil attack~\cite{douceur2002sybil} prevention mechanism moves from the blockchain backbone to the application layer.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

>>>>

The decentralised and democratic nature of blockchain technology removes central point of control or failure.
However, as we described in the Introduction, it faces a genuine scalability problem.
In particular, proof-of-work based systems are unlikely to reach the transaction rate of Visa even with parameter tuning.
What we wish to see is horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
Hence, the research question we answer in this  work is the following.
\begin{displayquote}
\emph{How do we design a blockchain fabric that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}

In order to make sense of our research question, we must first define \emph{blockchain fabric}.
Typical blockchain systems are application specific.
For example, the application in Bitcoin (any many of its derivatives) is digital cash, the application in Namecoin is domain name registration~\cite{namecoin} and the application in Siacoin is cloud storage~\cite{siacoin}.
Underneath these applications lies the blockchain fabric which has the goal of reaching consensus on transactions.
In the case of Bitcoin it is proof-of-work (PoW).
It is not concerned with the structure of the transactions,
it works by simply treating transactions as a blob of data and hashes them with the previous block.
Hence, we focus on blockchain fabric rather than any specific application.
Because it is the scalability bottleneck and is neccessary for any blockchain based application.
% Also, it should be possible to build any kind of application on top our system.
% We do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

In the remainder of this chapter we expand on our research question and visit each of our requirement in detail.

@@

% why consensus is important
% The first objective is to reach consensus on a global \emph{state}.
% We emphasise the word state because in contrary to traditional blockchains,
% it does not neccessarily mean the set of all transactions that has ever happened.
% The state can be a verifiable representation of all the transactions.
% As an extreme example, a single digest of the complete history can represent the state.
% It is even verifiable as long as there are nodes that stores the history.

Early blockchain systems use PoW as the consensus algorithm,
but consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
consensus algorithms have existece since the 80s~\cite{pease1980reaching, lamport1982byzantine}.
The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
The authors show that running PBFT in Network File System (NFS) was only 3\% slower than the standard unreplicated NFS.
Since then, research in this area picked up pace and many more algorithms are introduced~\cite{abd2005fault, kotla2007zyzzyva}.
With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

The first objective is to reach consensus on a global \emph{state} by standing on the shoulder of giants.
Having consensus is essential in blockchain systems.
It stops many types of malicious activities because agreed state must have the consent of the honest nodes in the network.
We emphasise the word state because in contrary to traditional blockchains,
it does not neccessarily mean the set of all transactions that has ever happened.
The state can be a verifiable representation of all the transactions.
As an extreme example, a single digest of the complete history can represent the state.
It is even verifiable as long as there are nodes that stores the history.

% Our approach is to combine the vast literature in Byzantine fault tolerance research with blockchain technology,
% and introduce a new consensus model to record the global state.

@@

There is another aspect of fault tolerance that is transaction verifiability.
All transactions must be eventually verifiable to maintain system integrity.
Further, the validation result must be consistent.
For example, if two different honest nodes attempts verify the same transaction,
it cannot be the case that one nodes thinks that the transaction is valid but the other thinks it is invalid.

% Recall that it is not neccessary to reach consensus on all the transactions in order to record the state.
% But when using some digest (or a set of digets) to represent the state, it is also important for the transactions to be verifiable.
% Otherwise adversaries could simply store invalid transactions in the state and they would never be detected.

@@

The last but not least, the final objective is horizontal scalability.
We wish to see the performance (global transaction rate) increase as more nodes join the network.
BitTorrent~\cite{cohen2003incentives} is an example of such a system,
where peers interact with each other to exchange files without any global bottleneck.

@@

\section{Limitations}
Our work aims to significantly lower the transaction bound.
However, the price to pay is that the Sybil attack~\cite{douceur2002sybil} prevention mechanism moves from the blockchain fabric to the application layer.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

### 2017-07-13 thesis/chapters/ch3-model.tex
Thanks Quinten

We present a design which removes the transaction rate restrictions seen in traditional blockchain systems.
This is done by combining the recent HoneyBadgerBFT~\cite{miller2016honey}
(a purely asynchronous consensus algorithm for blockchain systems)
with a modification of our prior work on TrustChain~\cite{trustchain}.
The design is inspired by the essence the (early) Internet architecture as well as how transactions are performed in the real world.

@@

Our subprotocol design gives us the highly desireable non-blocking property.
In particular, we do not need to ``freeze'' the state of the chain for some communication to complete in order to create a block.
For instance, a node may start the consensus protocol, and while it is running, create new transactions and validate old transactions.
By the time the consensus protocol is done, the new CP block is added to whatever the state that the chain is in.
It is not necessary to keep the chain immutable while the consensus protocol is running.

@@

We assume purely asynchronous channels with eventual delivery.
Thus in no circumstance do we make timing assumptions.
The adversary has fully control of the delivery schedule and the message ordering.
But they are not allowed to drop messages\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
}.

@@

Our threat model is as follows. 
We use a restricted version of the adaptive corruption model.
The first restriction is that corrupted node can only change across rounds.
That is, if a round has started, the corrupted nodes cannot changed until the next round.
The second restriction is that the adversary, presumably controlling all the corrupted nodes, is forgetful.
Namely the adversary may learn the internal state such as the private key of a corrupted node,
but if the node recovers, then the adversary must forget the private key.
Otherwise the adversary can eventually learn all the private keys and sabotage the system.
Finally, we assume computational security.
That is, the adversary can run polynomial-time algorithms but not exponential-time algorithms.

@@

\subsection{Transaction Block}
The TX block is a six-tuple, i.e $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$.
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatination of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

@@

\subsection{Validation Protocol}
With the validity definition, we are ready to construct a protocol for determining the validity of transactions.
The protocol is a simple response and request protocol (\Cref{alg:vd-proto}).
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Consensus on transactions}}

@@

An optimisation we can do is to use an epidemic protocol~\cite{eugster2004epidemic} (also known as gossiping)) instead of our broadcast approach.
Typical epidemic protocols works as follows.
Every node buffers every message it receives up to some buffer size $b$.
Then it forwards the messages $t$ number of times.
Every time the message is sent to $f$ random neighbours, $f$ is often called the fan-out.
The upside of using epidemic protocol is a lower communication cost.
This is especially true with a lazy push approach the node who just received a message would push the message ID to its $f$ random neighbours,
and only push the full message if the neighbour explicitly requests for the message~\cite{leitao2007epidemic}.
With this, nodes typically only need to receive one consensus result message instead of $n$.

A down side of epidemic protocol is that it usually takes $O(\log N)$ time to infect the whole network,
whereas broadcasting uses constant time.
Another downside of some epidemic protocols (e.g. eager push) is that it is difficult to guarantee delivery.
It is especially true when the parameters are not choosen correctly of if the network is not fully connected.
If the delivery cannot be guaranteed, 
then we cannot guarantee liveness in our consensus protocol because a future facilitator may miss the memo.
Picking parameters are difficult in practice because the network configuration is unknown and the total number of nodes might also be unknown.

>>>>

We present a design which removes the transaction rate restrictions seen in traditional blockchain systems.
This is done by combining the recent HoneyBadgerBFT~\cite{miller2016honey}
(a purely asynchronous consensus algorithm for blockchain systems)
with a modification of our prior work on TrustChain~\cite{trustchain}.
The design is inspired by (the distributed part of) the Internet architecture as well as how transactions are performed in the real world.

@@

Our subprotocol design gives us the highly desireable non-blocking property.
In particular, we do not need to ``freeze'' the state of the chain for some communication to complete in order to create a block.
For instance, a node may start the consensus protocol, and while it is running, create new transactions and validate old transactions.
By the time the consensus protocol is done, the new CP block is added to whatever the state that the chain is in.
It is not necessary to lock the chain while the consensus protocol is running and then unlock it afterwards.

@@

We assume purely asynchronous channels with eventual delivery.
Thus in no circumstance do we make timing assumptions.
The adversary has fully control of the delivery schedule and the message ordering of all messages.
But they are not allowed to drop messages except for their own\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
}.

@@

Our threat model is as follows. 
We use a restricted version of the adaptive corruption model.
The first restriction is that corrupted node can only change across rounds.
That is, if a round has started, the corrupted nodes cannot changed until the next round.
The second restriction is that the adversary, presumably controlling all the corrupted nodes, is forgetful.
Namely the adversary may learn the internal state such as the private key of a corrupted node,
but if the node recovers, then the adversary must forget the private key.
This is realistic because otherwise the adversary can eventually learn all the private keys and sabotage the system.
Finally, we assume computational security.
That is, the adversary can run polynomial-time algorithms but not exponential-time algorithms efficiently.

@@

\subsection{Transaction Block}
The TX block is a six-tuple, i.e $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$.
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatination of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

@@

\subsection{Validation Protocol}
With the validity definition, we are ready to construct a protocol for determining the validity of transactions.
The protocol is a simple response and request protocol (\Cref{alg:vd-proto}).
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

An optimisation we can do is to use an epidemic protocol~\cite{eugster2004epidemic} (also known as gossiping)) instead of our broadcast approach.
Typical epidemic protocols works as follows.
Every node buffers every message it receives up to some buffer size $b$.
Then it forwards the messages $t$ number of times.
Every time the message is sent to $f$ random neighbours, $f$ is often called the fan-out.
The upside of using epidemic protocol is that the communication cost is distributed more evenly between nodes.
This is especially true with a lazy push approach the node who just received a message would push the message ID to its $f$ random neighbours,
and only push the full message if the neighbour explicitly requests for the message~\cite{leitao2007epidemic}.
With this, nodes typically only need to receive one consensus result message instead of $n$.

A down side of epidemic protocol is that it usually takes $O(\log N)$ time to infect the whole network,
whereas broadcasting uses constant time.
Another downside of some epidemic protocols (e.g. eager push) is that it is difficult to guarantee delivery.
It is especially true when the parameters are not choosen correctly in a network that is only partially connected (but every node is nevertheless reachable).
If the delivery cannot be guaranteed, 
then we cannot guarantee liveness in our consensus protocol because a future facilitator may miss the memo.
Picking parameters are difficult in practice because the network configuration is unknown and the total number of nodes might also be unknown.

### 2017-07-13 thesis/chapters/ch4-analysis.tex
Thanks Quinten

Up to this point we described our system specification in detail.
Of course, specification along does not establish any truths.
In this chapter, we analyse two aspects of our system.
First we show it has the desired properties.
That is, the properties in \Cref{def:consensus} and \Cref{def:validation} should hold.
Then we analyse the performance, especially the throughput,
and show that it out performs classical blockchain systems.

@@

For the inductive step,
we assume that the 4 properties hold in round $r$ and prove that they also hold in round $r + 1$.
Using Lemmas \ref{lemma:agreement}, \ref{lemma:validity}, \ref{lemma:fairness} and \ref{lemma:termination},
it directly follows from Modus Poneus that these properties hold for $r + 1$.
Due to the principals of mathematical induction, these properties hold for all $r$.
\end{proof}

>>>>

Up to this point we described our system specification in detail.
Of course, specification along does not establish any truths.
In this chapter, we analyse two aspects of our system.
First we show it has the desired properties.
That is, the properties of the consensus protocol and the validation protocol (\Cref{def:consensus} and \Cref{def:validation} respectively) should hold.
Then we analyse the performance, especially the throughput,
and show that it out performs classical blockchain systems.

@@

For the inductive step,
we assume that the 4 properties hold in round $r$ and prove that they also hold in round $r + 1$.
Using Lemmas \ref{lemma:agreement}, \ref{lemma:validity}, \ref{lemma:fairness} and \ref{lemma:termination},
it directly follows from modus ponens that these properties hold for $r + 1$.
Due to the principals of mathematical induction, these properties hold for all $r$.
\end{proof}

### 2017-07-13 thesis/chapters/ch5-implementation.tex
Thanks Quinten

The prototype implementation can be found on GitHub\footnote{\url{https://github.com/kc1212/consensus-thesis-code}}.
It is written in the event driven paradigm, using the Python programming language\footnote{\url{https://www.python.org/}} and
the Twisted\footnote{\url{https://twistedmatrix.com/}} library for networking.

@@

\begin{figure}[h]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/timeseries}
    \caption{}
    \label{fig:backlog-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/timeseries}
    \caption{}
    \label{fig:backlog-random}
  \end{subfigure}
  }
  \caption{}
  \label{fig:backlog}
\end{figure}

>>>>

The prototype implementation can be found on GitHub.
\begin{displayquote}
\url{https://github.com/kc1212/consensus-thesis-code}
\end{displayquote}
It is written in the event driven paradigm, using the Python programming language\footnote{\url{https://www.python.org/}} and
the Twisted\footnote{\url{https://twistedmatrix.com/}} library for networking.

@@

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/timeseries}
    \caption{}
    \label{fig:backlog-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/timeseries}
    \caption{}
    \label{fig:backlog-random}
  \end{subfigure}
  }
  \caption{}
  \label{fig:backlog}
\end{figure}
